\begin{thebibliography}{00}
\bibitem{tian2025metahp} Z.~Tian, Y.~Liu, and Q.~Sun, ``Meta-Learning Hyperparameters for Parameter Efficient Fine-Tuning,'' in \emph{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 2025, pp. 23037--23047.
\bibitem{dosovitskiy2021vit} A.~Dosovitskiy \emph{et~al.}, ``An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale,'' in \emph{International Conference on Learning Representations (ICLR)}, 2021.
\bibitem{hu2022lora} E.~Hu \emph{et~al.}, ``LoRA: Low-Rank Adaptation of Large Language Models,'' in \emph{International Conference on Learning Representations (ICLR)}, 2022.
\bibitem{houlsby2019adapter} N.~Houlsby \emph{et~al.}, ``Parameter-Efficient Transfer Learning for NLP,'' in \emph{International Conference on Learning Representations (ICLR)}, 2019.
\bibitem{finn2017maml} C.~Finn, P.~Abbeel, and S.~Levine, ``Model-Agnostic Meta-Learning for Fast Adaptation of Deep Networks,'' in \emph{International Conference on Machine Learning (ICML)}, 2017.
\bibitem{ren2018reweight} M.~Ren, W.~Zeng, B.~Yang, and R.~Urtasun, ``Learning to Reweight Examples for Robust Deep Learning,'' in \emph{International Conference on Machine Learning (ICML)}, 2018.
\bibitem{jamal2020class} M.~A. Jamal, L.~E. Shafey, and M.~M. Alam, ``Learning Class-bias in Multiclass Imbalanced Data,'' in \emph{IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}, 2020.
\bibitem{hendrycks2017baseline} D.~Hendrycks and K.~Gimpel, ``A Baseline for Detecting Misclassified and Out-of-Distribution Examples in Neural Networks,'' in \emph{International Conference on Learning Representations (ICLR)}, 2017.
\end{thebibliography}
